The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-27 paper.Rmd
added Appendix

>>>>

# Appendix

## R Code for [4.1 Photodimerization Simulation](#sec-Photodimerization)

```{r a1, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
# Load required libraries
if (!require("reshape2")) install.packages("reshape2")
if (!require("ggplot2")) install.packages("ggplot2")
library(reshape2)
library(ggplot2)
# Define reaction rates
c1 <- (37 / 1e6) * 10             # Formation of CPD
c2 <- (2 / 1e6) * 10              # Formation of 64-PP
# Initial state
state <- c(T1 = 10000, T2 = 10000, CPD = 0, `64PP` = 0)
# Define propensity functions
propensities <- function(state) {
  c(
    c1 * state["T1"] * state["T2"], # Reaction 1
    c2 * state["T1"] * state["T2"]  # Reaction 2
  )
}
# Gillespie simulation function
simulate_gillespie <- function(state, max_time) {
  # Initialize time and output data frame
  time <- 0
  output <- data.frame(
    Time = numeric(0),
    T1 = numeric(0),
    T2 = numeric(0),
    CPD = numeric(0),
    `64PP` = numeric(0)
  )

  # Convert columns to numeric for consistency
  output[] <- lapply(output, as.numeric)
  return(output)
}
# Run the simulation
max_time <- 100
simulation <- simulate_gillespie(state, max_time)

# Reshape data for plotting
simulation_long <- melt(simulation, id.vars = "Time")
# Plot results
ggplot(simulation_long, aes(x = Time, y = value, color = variable)) +
  geom_line() +
  labs(
    x = "Time",
    y = "Molecule Count",
    color = "Species"
  ) +
  theme_minimal()
```

## R code for [4.2 Radioactive Decay Simulation](#sec-Decay)
```{r a2, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
# Define parameters
c <- 0.01  # Decay rate constant
state <- c(R = 10000)  # Initial radioactive substance
max_time <- 1000  # Extended maximum simulation time

# Linear-scale plot
ggplot(simulation, aes(x = Time, y = R)) +
  geom_line(color = "blue") +
  labs(
    x = "Time",
    y = "Remaining Radioactive Substance (R)"
  ) +
  theme_minimal()

# Logarithmic-scale plot
ggplot(simulation, aes(x = Time, y = R)) +
  geom_line(color = "red") +
  scale_y_log10() +
  labs(
    x = "Time",
    y = "Remaining Radioactive Substance (log(R))"
  ) +
  theme_minimal()
